Meta-analysis

### 2020-02-24 04_MetaAnalysis.Rmd
Apply theme_usq() globally

```{r MEsummary_Libraries2, message=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, bomrang, lme4, RColorBrewer)

@@

slimmer_PM_dat %>%
   ggplot(aes(y = grain_yield.t.ha, x = spray_management)) +
   geom_boxplot() +
   #geom_point(position = "jitter", alpha = 1/5)+
   geom_jitter(width = 0.1, alpha = 1 / 5) +
   theme_usq() +
   labs(x = "Spray management variable",
        y = "Grain yield (t/Ha)",
        title = "Mean grain yield from each treatment \n categorised by spray management scenario") +
   theme(plot.title = element_text(hjust = 0.5)) +
   geom_hline(yintercept = 0, linetype = 2) +
   coord_flip()
```

@@

slimmer_PM_dat %>%
   ggplot(aes(y = prop_yield_gain, x = spray_management)) +
   geom_boxplot() +
   #geom_point(position = "jitter", alpha = 1/5)+
   geom_jitter(width = 0.1, alpha = 1 / 5) +
   theme_usq() +
   labs(x = "Spray management variable",
        y = "Grain yield (t/Ha)",
        title = "Mean grain yield from each treatment \n categorised by spray management scenario") +
   theme(plot.title = element_text(hjust = 0.5)) +
   geom_hline(yintercept = 0, linetype = 2) +
   coord_flip()
```

@@

efficacy %>%
   ggplot(aes(Treatment, Mean)) +
   geom_hline(
      yintercept = c(0.8, 1, 1.2, 1.4),
      color = "grey80",
      linetype = 3
   ) +
   geom_point(aes(size = 1 / SE), shape = 15) +
   geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper)) +
   coord_flip() +
   theme_usq()
```

>>>>

```{r MEsummary_Libraries2, message=FALSE, include=FALSE}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, bomrang, lme4, RColorBrewer)

@@

slimmer_PM_dat %>%
   ggplot(aes(y = grain_yield.t.ha, x = spray_management)) +
   geom_boxplot() +
   #geom_point(position = "jitter", alpha = 1/5)+
   geom_jitter(width = 0.1, alpha = 1 / 5) +
   labs(x = "Spray management variable",
        y = "Grain yield (t/Ha)",
        title = "Mean grain yield from each treatment \n categorised by spray management scenario") +
   theme(plot.title = element_text(hjust = 0.5)) +
   geom_hline(yintercept = 0, linetype = 2) +
   coord_flip()
```

@@

slimmer_PM_dat %>%
   ggplot(aes(y = prop_yield_gain, x = spray_management)) +
   geom_boxplot() +
   #geom_point(position = "jitter", alpha = 1/5)+
   geom_jitter(width = 0.1, alpha = 1 / 5) +
   labs(x = "Spray management variable",
        y = "Grain yield (t/Ha)",
        title = "Mean grain yield from each treatment \n categorised by spray management scenario") +
   theme(plot.title = element_text(hjust = 0.5)) +
   geom_hline(yintercept = 0, linetype = 2) +
   coord_flip()
```

@@

efficacy %>%
   ggplot(aes(Treatment, Mean)) +
   geom_hline(
      yintercept = c(0.8, 1, 1.2, 1.4),
      color = "grey80",
      linetype = 3
   ) +
   geom_point(aes(size = 1 / SE), shape = 15) +
   geom_linerange(aes(ymin = CIs_lower, ymax = CI_upper)) +
   coord_flip()
```
